A python toolbox to tackle the curse of imbalanced datasets in machine learning

### 2016-06-18 main.tex
go on

\begin{abstract}
\emph{UnbalancedDataset} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
The state-of-the-art methods implemented can be categorized into 4 different sampling strategies: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
The proposed toolbox depends of \emph{numpy}, \emph{scipy}, and \emph{scikit-learn}.
The implementation pattern is identical to the \emph{scikit-learn} API to offer compatibility.
Documentation, unit tests as well as integration tests are provided to allow new developers to contribute.
The toolbox is publicly available in GitHub \url{https://github.io} as well as the documentation \url{https://github.io}.
\end{abstract}

@@

@@

\section{Sustainability and continuous integration}

\begin{description}
  \item[Documentation]
  \item[Unit tests]
  \item[Integration tests]
\end{description}

@@

>>>>

\begin{abstract}
\emph{UnbalancedDataset} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
The state-of-the-art methods implemented can be categorized into 4 different sampling strategies: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
The proposed toolbox only depends of \emph{numpy}, \emph{scipy}, and \emph{scikit-learn} and is distributed under MIT license.
The implementation pattern is identical to the \emph{scikit-learn} API to offer compatibility.
Documentation, unit tests as well as integration tests are provided to allow new developers to contribute.
The toolbox is publicly available in GitHub \url{https://github.com/fmfn/UnbalancedDataset} as well as the documentation \url{https://github.io}.
\end{abstract}

@@

\section{Project management}

\begin{description}
  \item[Quality insurance] In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1 of the toolbox. Furthermore, the code quality is ensured by following \texttt{PEP8} standard and each contribution is automatically check through landscape.
  \item[Continuous integration]
  \item[Documentation]
\end{description}

@@

@@

\acks{We would like to acknowledge support for this project
from GitHub, Travis CI, and Gitter.}
